\documentclass[../main.tex]{subfiles}

\begin{document}
	\section{Income and Equity}
	
	\subsection{Corporations}
	
	The corporate form of organization has several advantages. The major 
	advantage is the ease of raising large amounts of money because both large 
	and small investors can participate in corporate ownership. It is simple to 
	become an owner of corporate shares of stock and just as simple to sell 
	these shares in organized exchanges such as the New York Stock Exchange 
	(NYSE), Singapore Stock Exchange etc. These exchanges maintain markets in 
	which shares are bought and sold each business day. 
	
	Corporations are entities created by law that exists separately from their 
	owners and that have rights and privileges. As separate entities, 
	corporations can:
	\begin{itemize}[noitemsep]
		\item Own assets
		\item Incur liabilities
		\item Sue and be sued.
		\item Enter into contracts. Shareholders are not agents of the 
		corporation and cannot enter into contracts on the corporation's 
		behalf. 
	\end{itemize}
	Shareholder losses are also limited in the amounts invested in the 
	corporation and corporate creditors cannot make claims on the personal 
	assets of shareholders to satisfy corporate debt.
	
	The corporate  form of organization has several advantages:
	\begin{itemize}[noitemsep]
		\item It is a separate legal entity that can enter into contracts and 
		sue or be sued. 
		\item Shareholder losses are limited to the amount invested in the 
		corporation.
		\item Ownership rights are transferable. 
		\item The corporation continues in existence even when ownership 
		changes. 
		\item Shareholders are not agents of the corporation and cannot enter 
		into contracts on the corporation's behalf. 
		\item Capital needs can be made by selling more ownership in the 
		corporation. 
	\end{itemize}
	The disadvantages include:
	\begin{itemize}[noitemsep]
		\item Extra governmental regulations imposed on corporations and 
		corporate taxation of earnings. Corporations pay taxes on their 
		earnings and if they distribute a dividend to shareholders, the 
		shareholders pay taxes on the dividends earned. 
	\end{itemize}
	
\end{document}